Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
remove extensions from appendix

%-------------------------------
\section{Extensions}
\label{sec:extensions}
%-------------------------------

%-------------------------------
\subsection{LTI systems with output} 
\label{ssec:LTI}
%-------------------------------

LTI models in the form: 
%
\begin{align}
\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
\vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
\end{align}
\noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
$\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
a continuous plant. Eq.~\eqref{eq:ode} is soundly discretized 
(as shown in the appendix) into
%
\begin{align}
\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k .\nonumber
\end{align}
%
\end{document}

>>>>

% %-------------------------------
% \section{Extensions}
% \label{sec:extensions}
% %-------------------------------

% %-------------------------------
% \subsection{LTI systems with output} 
% \label{ssec:LTI}
% %-------------------------------

% LTI models in the form: 
% %
% \begin{align}
% \dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
% \vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
% \end{align}
% \noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
% $\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
% a continuous plant. Eq.~\eqref{eq:ode} is soundly discretized 
% (as shown in the appendix) into
% %
% \begin{align}
% \vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
% \vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k .\nonumber
% \end{align}
%
\end{document}
